Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-09-19 paper/re-pro-badge.tex

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/9c36faf}{9c36faf} on 2024-09-07 at 07:01:11 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/9a5f9ad}{9a5f9ad} on 2024-09-10 at 13:14:05 UTC.
